%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Xmartlab} % Organization
    {Santiago, Chile} % Location
    {May. 2018 - PRESENT} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implement a large-scale data extraction mechanism.}
        \item {Automate data processing pipelines in an efficient and scalable way.}
        \item {Build micro data processing services using AWS Lambda, API Gateway, S3 and RDS.}
        \item {Design and implement a storage architecture for heterogeneous and unstructured data.}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Data Scientist} % Job title
    {Smartbots, spinoff of 2Brains} % Organization
    {Santiago, Chile} % Location
    {Aug. 2017 - May. 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Promote the different lines of business based on the data. These lines mainly corresponded to retail and banking. Participation in:}
      	\begin{itemize}
        	\item{Product recommendation for retail.}
        	\item{Characterization of customers.}
        	\item{Web Scraping of different social networks related to IT professionals.}
        	\item{Predictive model that allows to determine if a profile will match with the company based on the public information of its profile of social networks and the evaluation to candidates with similar characteristics.}
        	\item{Identification of the main intentions within thousands of conversations in different sources of information.}
        	\item{Automation of the design process in conversational flows.}
        	\item{Construction of metrics and visualizations to measure performance, seasonality of bots use.}
      	\end{itemize}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {2Brains} % Organization
    {Santiago, Chile} % Location
    {May. 2017 - Aug. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implementation of software components using JAVA for the sales force services of a bank.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Engineer} % Job title
    {Ticblue} % Organization
    {Santiago, Chile} % Location
    {Jul. 2015 - May. 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Design and implementation of software components using back-end technologies (mainly Ensemble by InterSystems and JAVA EE).}
        \item {Design of solutions under a vision of service-oriented architecture (SOA).}
        \item {Administration and exploitation of high performance database engine.}
        \item {Construction of integration components.}
        \item {Exploiting the transaction messaging of the ESB using BI tools.}
        \item {Construction of integration components.}
        \item {Integration between services of institutions (Registro Civil, Ministerio de Desarrollo Social and JUNJI) for the application process of postulants.}
        \item {Automation of information replacement activities, for remuneration payments of a government entity with more than 30,000 employees.}
        \item {Build Concepts Tests (POC) to support sales processes about real problems of potential clients.}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
